%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Ziad Hany Mohammed} \\ 
       \vspace{5pt}
    {\Large \textbf{Backend Developer} \hspace{15pt} $|$ \hspace{15pt} Tanta , Egypt} \\ 
    \vspace{5pt}
    \small 
    \raisebox{-0.1\height}\faPhone\ +20 01554530991 ~ 
    \href{mailto:ziadhani64@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{ziadhani64@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/ziad-hani/}{\raisebox{-0.2\height}\faLinkedin\ \underline{ziad-hani}} ~ 
    \href{https://github.com/ziadhanii}{\raisebox{-0.2\height}\faGithub\ \underline{ziadhanii}}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tanta University}{Aug. 2021 -- Aug 2024}
      {Bachelor of Computer Science — GPA: 3.0/4.0}{Tanta, Egypt}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    \begin{multicols}{3}
        \begin{itemize}[itemsep=-5pt, parsep=3pt]
            \item \small Data Structures
            \item Software Engineering
            \item Algorithms Analysis
            \item Database Management
            \item Artificial Intelligence
            \item Internet Technology
            \item Systems Programming
            \item Computer Architecture
            \item Machine Learning
        \end{itemize}
    \end{multicols}
    \vspace*{2.0\multicolsep}
    
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
    {Information Technology Institute, ITI $|$ \hspace{5pt} \textcolor{blue}{\href{https://link_to_certificate}{Link}}}{August 2024 -- September 2024}
    {Backend (.NET) Intern}{Menofia, Egypt}
    \resumeItemListStart
      \resumeItem{Studied C\# programming language, covering foundational and advanced topics including Object-Oriented Programming (OOP), LINQ, and advanced C\# features.}
      \resumeItem{Learned database concepts using SQL Server, including ERD (Entity-Relationship Diagram) design, database mapping, and implementation with SQL.}
      \resumeItem{Worked with Entity Framework Core for database interactions, focusing on handling CRUD operations, data querying, and performance optimization.}
      \resumeItem{Developed web applications using the MVC (Model-View-Controller) pattern in ASP.NET Core, implementing a full-stack project from scratch.}
      \resumeItem{Implemented RESTful APIs to connect front-end components with back-end logic and ensure efficient data flow.}
      \resumeItem{Gained insights into freelancing, identifying service offerings, and developing a pricing structure for web development projects.}
      \resumeItem{Learned project management essentials, including portfolio creation, personal branding, and writing successful proposals for client engagement.}
    \resumeItemListEnd

  \resumeSubheading
  {Apps Square Academy Training $|$ \hspace{5pt} \textcolor{blue}{\href{https://drive.google.com/file/d/1TZwE-7JMcJ-a1B46s2ioIn3uSYnJayZx/view?usp=drive_link}{Link}}}{July 2024 -- September 2024}
  {Backend (.NET) Intern}{Tanta, Egypt}
    \resumeItemListStart
      \resumeItem{Developed RESTful APIs using ASP.NET Core, applying the CQRS and Repository Pattern to manage complex business logic and data access.}
      \resumeItem{Utilized Entity Framework Core for database management, handling CRUD operations and optimizing data queries.}
      \resumeItem{Implemented JWT (JSON Web Token) based authentication for secure access and role-based authorization within the application.}
      \resumeItem{Followed Clean Architecture principles to maintain separation of concerns, improve scalability, and enhance code maintainability.}
      \resumeItem{Integrated Serilog for structured logging, capturing user actions, errors, and system warnings, and Hangfire for background task processing and scheduling.}
      \resumeItem{Designed and analyzed Entity Relationship Diagrams (ERDs) to create efficient database schemas, improving data consistency and integrity.}
      \resumeItem{Worked extensively with ASP.NET Identity for user management, secure authentication, and role-based authorization.}
      \resumeItem{Configured automated logging and real-time monitoring of background jobs using Hangfire and Serilog to enhance application observability and error tracking.}
      \resumeItem{Successfully completed an evaluation task: \textbf{Boat and Trip Booking System}, where I designed and implemented a full-stack booking platform featuring authentication, logging, data management, and robust error handling, following best practices in .NET software architecture.}
    \resumeItemListEnd

  \resumeSubheading
  {National Telecommunication Institute, NTI $|$ \hspace{5pt} \textcolor{blue}{\href{https://drive.google.com/file/d/1lvcHiExjEDObHDEzapaIxWdP3OGyv8nf/view?usp=drive_link}{Link}}}{August 2024 -- September 2024}
    {Web Design and Development Intern}{Cairo, Egypt}
    \resumeItemListStart
      \resumeItem{Studied web development concepts, focusing on HTML, CSS, JavaScript, and Bootstrap to build responsive and visually appealing websites.}
      \resumeItem{Explored UI/UX design principles to enhance user experience and website functionality.}
      \resumeItem{Worked with back-end integration, utilizing RESTful APIs to connect front-end components to server-side functionality.}
      \resumeItem{Gained insights into freelancing, identifying service offerings, and developing a pricing structure for web development projects.}
      \resumeItem{Learned essentials of project management, portfolio creation, personal branding, and delivering successful proposals.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
\vspace{-5pt}
\resumeSubHeadingListStart
  \resumeProjectHeading
      {\textbf{Boat and Trip Booking System} $|$ \emph{RESTful API, Entity Framework, SQL Server} $|$ \textcolor{blue}{\href{https://github.com/ziadhanii/boat-rental-system}{GitHub}}}{September 2024}
      \resumeItemListStart
        \resumeItem{Developed a comprehensive booking platform for boats and trips, supporting Admin, Owner, and Customer roles.}
        \resumeItem{Implemented JWT-based authentication and authorization for enhanced API security.}
        \resumeItem{Applied the CQRS pattern to separate read and write operations, utilizing the Repository Pattern for effective data abstraction.}
        \resumeItem{Employed Serilog for logging, capturing critical events and errors.}
        \resumeItem{Integrated a robust error-handling mechanism to manage exceptions and provide user-friendly feedback.}
        \resumeItem{Delivered organized source code with comprehensive API documentation, SQL scripts for the database schema, and a detailed README file.}
      \resumeItemListEnd 
      \vspace{-13pt}
  
  \resumeProjectHeading
      {\textbf{Talabat Full Stack} $|$ \emph{RESTful API, Angular, Rider, VS Code, Postman} $|$ \textcolor{blue}{\href{https://github.com/yourusername/talabat-fullstack}{GitHub}}}{June 2024}
      \resumeItemListStart
        \resumeItem{Developed a secure back-end system for an E-Commerce website.}
        \resumeItem{Implemented JWT for authentication and authorization.}
        \resumeItem{Designed data models and enforced input validation to ensure data integrity.}
        \resumeItem{Maintained API consistency and usability by adhering to RESTful principles.}
        \resumeItem{Developed the front-end using Angular to enhance user experience.}
      \resumeItemListEnd
      \vspace{-13pt}
  
  \resumeProjectHeading
      {\textbf{Sending Emails with MailKit and MimeKit} $|$ \emph{C\#, .NET, MailKit, MimeKit} $|$ \textcolor{blue}{\href{https://github.com/ziadhanii/sending-emails-with-mailkit-and-mimekit}{GitHub}}}{September 2024}
      \resumeItemListStart
        \resumeItem{Created a .NET example for sending emails using MailKit and MimeKit.}
        \resumeItem{Demonstrated sending basic email messages, attaching files, and sending HTML content.}
        \resumeItem{Included easy-to-follow examples and asynchronous email sending features.}
      \resumeItemListEnd 
      \vspace{-13pt}
  
  \resumeProjectHeading
      {\textbf{Game Zone} $|$ \emph{ASP.NET Core, Visual Studio, SSMS} $|$ \textcolor{blue}{\href{https://github.com/yourusername/game-zone}{GitHub}}}{March 2024}
      \resumeItemListStart
        \resumeItem{Developed a web application using the MVC architecture with ASP.NET Core 8 to manage video games.}
        \resumeItem{Implemented robust CRUD operations for managing game data in a database.}
      \resumeItemListEnd 
      \vspace{-13pt}
  
  \resumeProjectHeading
      {\textbf{Postman Clone App} $|$ \emph{C\#, .NET 8, WinForms, HttpClient} $|$ \textcolor{blue}{\href{https://github.com/ziadhanii/postman-clone-app}{GitHub}}}{August 2024}
      \resumeItemListStart
        \resumeItem{Developed a tool for developers and testers to simplify HTTP requests to APIs and view responses in formatted JSON.}
        \resumeItem{Implemented a user-friendly interface to streamline API interactions and debugging.}
        \resumeItem{Facilitated efficient validation and troubleshooting of API calls.}
      \resumeItemListEnd 
      \vspace{-13pt}
  
  \resumeProjectHeading
      {\textbf{Euro 2024 Results} $|$ \emph{Blazor Web Assembly} $|$ \textcolor{blue}{\href{https://github.com/ziadhanii/euro-2024-results-using-blazor-web-assembly}{GitHub}}}{June 2024}
      \resumeItemListStart
        \resumeItem{Developed a web application to display Euro 2024 results using Blazor Web Assembly.}
        \resumeItem{Implemented interactive features to enhance user engagement.}
        \resumeItem{Utilized GitHub for version control and project management.}
      \resumeItemListEnd 
      \vspace{-13pt}
  
  \resumeProjectHeading
      {\textbf{Warsha MVC - ITI Graduation Project} $|$ \emph{ASP.NET Core, MVC, SQL Server} $|$ \textcolor{blue}{\href{https://github.com/ziadhanii/iti-graduation-project-warsha-mvc}{GitHub}}}{September 2024}
      \resumeItemListStart
        \resumeItem{Developed a web application for managing and connecting freelancers with clients using ASP.NET Core MVC.}
        \resumeItem{Implemented user authentication and role-based access control.}
        \resumeItem{Designed the database schema and implemented CRUD functionalities for project listings.}
        \resumeItem{Utilized GitHub for version control and collaborative development.}
      \resumeItemListEnd 
      \vspace{-13pt}
  
  \resumeProjectHeading
      {\textbf{Stopwatch GUI Program} $|$ \emph{Java, OOP, IntelliJ, JavaFX} $|$ \textcolor{blue}{\href{https://github.com/yourusername/stopwatch-gui}{GitHub}}}{November 2022}
      \resumeItemListStart
        \resumeItem{Designed a sample Stopwatch application using Java.}
        \resumeItem{Utilized JavaFX to create a user-friendly GUI.}
        \resumeItem{Implemented object-oriented programming practices, including inheritance.}
      \resumeItemListEnd 
\resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \small{\textbf{Languages:} C\#, C++, Java, HTML, CSS, JavaScript, SQL}
    \item \small{\textbf{Frameworks:} ASP.NET Core (MVC, API), .NET (6 - 9), Blazor, Windows Forms, Entity Framework Core}
    \item \small{\textbf{Technologies:} RESTful APIs, Microservices, Docker, Bootstrap}
    \item \small{\textbf{Databases:} SQL Server, PostgreSQL, MySQL, NoSQL (MongoDB)}
    \item \small{\textbf{Development Tools:} Visual Studio, Rider, VS Code, Postman, Insomnia, SSMS, DataGrip, Azure Data Studio} 
    \item \small{\textbf{Concepts:} OOP, Data Structures, Algorithms, SDLC, Agile, Design Patterns, RDBMS, ORM, LINQ, Dependency Injection, Version Control (Git/GitHub), Unit Testing, CI/CD}
\end{itemize}
\vspace{-8pt}

%-----------CERTIFICATES-----------
\section{Certifications}
\resumeItemListStart
    \resumeItem{\textbf{Backend Development with ASP.NET Core} \\ Information Technology Institute}
    \resumeItem{\textbf{Backend (Dot Net)} $|$ \href{https://drive.google.com/file/d/1TZwE-7JMcJ-a1B46s2ioIn3uSYnJayZx/view?usp=drive_link}{Apps Square Academy}}
    \resumeItem{\textbf{Web Design} $|$ \href{https://drive.google.com/file/d/1lvcHiExjEDObHDEzapaIxWdP3OGyv8nf/view?usp=drive_link}{National Telecommunication Institute} \\ Summer Training Course 2024}
\resumeItemListEnd

%-----------INVOLVEMENT---------------
\section{Leadership / Extracurricular Activities}
\resumeSubHeadingListStart
    \resumeSubheading{Student Union of the College of Computers and Information}{Fall 2022 -- Present}
    {Chair of the Scientific Committee}{Tanta University}
    
    \resumeSubheading{"Family for Egypt" A Student Entity at University}{Fall 2023 -- Present}
    {Chair of the Scientific Committee}{Tanta University}

\resumeSubheading{Media Team on the Official Page of the Tanta Computer and Information Students Union}{}{Media Member \href{https://www.facebook.com/FCITUStudentUnion/posts/pfbid0gVqNnqsg43vtcHXkuPAr9RSEgsVUAijRtCCnKQdpnhQZYvBExtHMEteyF1bm4yjVl}{\faFacebookSquare}}{Tanta University}
\resumeItemListStart
    \resumeItem{Designed engaging social media graphics that boosted student engagement by 30\%.}
    \resumeItem{Collaborated with team members to create a strategic content calendar for regular and impactful posting.}
    \resumeItem{Analyzed social media metrics to optimize future campaigns and enhance outreach.}
\resumeItemListEnd

\resumeSubHeadingListEnd


\end{document}
